\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation \dg{for Machine Learning}

### 2018-05-06 ccs/conclude.tex
comments
reviews incorporate

\section{Conclusion and Future Work}
\label{sec:conclude}
We presented \tool, the first
cryptographic-cost aware framework that generates efficient and
scalable \mpc protocols from high-level programs.
The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to, or better than the custom, specialized
protocols from previous works.
The \mpc backed we use provides security against semi-honest or passive adversaries.
%our compiler is oblivious to the ``type of adversary'' for the underlying \mpc backend.
Given a \mpc backend secure against malicious or active adversaries, Theorem \ref{theorem:security} 
can be extended to obtain a framework with malicious security. Furthermore,  
partitioning can be modified to provide malicious security by {\it signing} the shares of the intermediate states. However, we are not aware of a maliciously secure \mpc implementation for combinations of
arithmetic and boolean circuits.

\dg{Add other future work such as language enhancement to support public inputs, declassification of intermediate values, secret array indices and support of ORAM. But since current focus was ML applications, didn't require these as such. Also, crypto backends would keep improving and although our ideas extend to works such as Gazelle, we leave integrating it as a backend in \tool as future work.}

>>>>

\section{Conclusion and Future Work}
\label{sec:conclude}
\dg{Make it consistent with contributions in intro.}
We presented \tool, the first
cryptographic-cost aware framework that generates efficient and
scalable \mpc protocols from high-level programs.
The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to, or better than the custom, specialized
protocols from previous works.
The \mpc backed we use provides security against semi-honest or passive adversaries.
%our compiler is oblivious to the ``type of adversary'' for the underlying \mpc backend.
Given a \mpc backend secure against malicious or active adversaries, Theorem \ref{theorem:security} 
can be extended to obtain a framework with malicious security. Furthermore,  
partitioning can be modified to provide malicious security by {\it signing} the shares of the intermediate states. However, we are not aware of a maliciously secure \mpc implementation for combinations of
arithmetic and boolean circuits.

\dg{Add other future work such as language enhancement to support public inputs, declassification of intermediate values, secret array indices and support of ORAM. But since current focus was ML applications, didn't require these as such. Also add functions. Also, crypto backends would keep improving and although our ideas extend to works such as Gazelle, we leave integrating it as a backend in \tool as future work.

We will explore the possibility of mechanically verifying the implementation of our compiler.

Tensorflow to \tool.}

### 2018-05-06 ccs/eval.tex
reviews incorporate

\setlength\tabcolsep{2.8pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Dataset & $d$  & \thead{Prev \\ time\\ (s)} & \thead{Prev \\ comm\\ (kb)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm \\(kb)}  &  \thead{Num \\ gates} & LOC\\
\hline
Breast cancer & 30 & 0.3 & 36 & 0.1 & 0.3 & 25  & 727 & 20\\
\hline
Credit & 47 & 0.3 & 41 & 0.1 & 0.3 & 36  & 795 & 20\\
\hline
\end{tabular}
 \caption{Linear classification results. We compare \tool (LAN, WAN, Comm)
 with~\cite{shafindss} (Prev time, Prev comm).}
 \label{tab:lc} 
\end{table}

@@

\setlength\tabcolsep{2.5pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c|c|c |c|c|c|c|}
\hline
Dataset & $n$ & $F$ & \thead{Prev \\ time\\ (s)} & \thead{Prev \\ comm\\ (kb)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm \\(kb)} & \thead{Num \\ gates}  & LOC\\
\hline
Nursery & 5 & 9 & 1.5 & 0.2 & 0.1 & 0.4 & 0.6  & 73k & 50\\
\hline
Audiology & 24 & 70 & 3.9 & 2.0 & 1.5 & 2.9 & 37  & 4219k & 50\\
\hline
\end{tabular}
\caption{Na\"{i}ve Bayes results. We compare \tool (LAN, WAN, Comm)
 with~\cite{shafindss} (Prev time, Prev comm).}
 \label{tab:nb} 
\end{table}

@@

\begin{table}[t]
\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
Dataset  & $d$ & $N$ & \thead{Prev \\ time\\ (s)} & \thead{Prev \\ comm\\ (kb)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm \\(kb)}& \thead{Num \\ gates} & LOC\\
\hline
Nursery & 4 & 4 & 0.3 & 102 & 0.1 & 0.3 & 32 & 3324 & 20\\
\hline
ECG & 4 &  6 & 0.4 & 102 & 0.1 & 0.4 & 49  & 5002 & 20\\
\hline
\end{tabular}
\caption{Decision tree benchmarks.We compare \tool (LAN, WAN, Comm)
 with~\cite{wu} (Prev time, Prev comm).}
 \label{tab:dt} 
\end{table}

@@

\setlength\tabcolsep{2.5pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c |c|c|c|c|c|}
\hline
DNN  & \thead{Prev \\ time\\ (s)} & \thead{Prev \\ comm\\ (kb)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm \\(kb)} & \thead{Num \\ gates} & \thead{Model\\ size} & LOC\\
\hline
SecureML   &  1.1 & 15.8 & 0.7 & 1.7  & 76   &   366k   & 119k & 78\\
\hline
Cryptonets &  1.3 & 47.6 & 0.6 & 1.6  & 70    &  316k & 86k & 88\\
\hline
CNN        &  9.4 & 657.5& 5.1 & 11.6 & 501  & 9480k & 35k & 154\\
\hline
\end{tabular}

@@

% benchmark | size | gates | and | mul | depth  | length | comm | timeL | timeW
\setlength\tabcolsep{2.5pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c |c|c|c|c|c|c | c}
\hline
Classifier       & \thead{LAN  \\ (s)} & \thead{WAN \\(s)} & \thead{Comm \\(Mb)}  & \thead{Num \\ And} & \thead{Num \\ Mul} & \thead{Num \\ gates} & \thead{Model \\size} & LOC\\
\hline
Regression &  0.1         & 0.7         & 5            & 2k    & 8k    &  35k    & 8k   & 38\\
\hline
CNN        &  30.5        & 60.3        & 2955         & 6082k & 4163k &  42104k & 3226k& 172\\
\hline
\end{tabular}

 \caption{Tensorflow tutorial benchmarks}
 \label{tab:tf} 
\end{table}
\setlength\tabcolsep{3.5pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c |c|c|c|c|c|c | c|}
\hline
Dataset       & \thead{LAN \\(s)} & \thead{WAN \\(s)} & \thead{Comm \\ (Mb)}  & \thead{Num \\ And} & \thead{Num \\ Mul} & \thead{Num \\ gates} & depth & LOC\\
\hline
Chars4k    &  0.1         & 0.7         & 2            & 18k    & 3k    &  85k     & 1   & 89\\
\hline
USPS       &  0.2         & 0.9         & 4            & 62k    & 2k    &  285k    & 2   & 156\\
\hline
WARD       &  0.3         & 1.1         & 9            & 106k    & 8k    &  506k    & 3   & 283\\
\hline
\end{tabular}

@@

\setlength\tabcolsep{6pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c |c|c|c|}
\hline
           &  LAN (s) & WAN (s) & \thead{Comm \\ (Mb)}  & \thead{Num \\ And} & \thead{Num \\ Mul} & \thead{Num \\ gates} \\
\hline
Total      &  265.6       & 647.5        & 40683       & 21m    & 61m    &  337m  \\
\hline
Stage 6    &  55.2        & 122.6        & 6744        & 12m    & 10m   &  98m  \\
\hline
\end{tabular}

@@

\begin{table}[t]
\footnotesize
\begin{tabular}{|c|c|c|c |c|c| c|}
\hline
  Stage         &  LAN (s) & WAN (s) & \thead{Comm \\ (Mb)}  & depth & \thead{Num \\ gates} & LOC\\
\hline
1    &  175       & 662        & 29816       & 16370    & 33m    & 500  \\
\hline
2    &  193        & 1095        & 31945        & 30916    & 37m & 516 \\
\hline
3    &  178        & 627        & 29810        & 16369    & 32m  & 478  \\
\hline
Total    &  546      & 2384        & 91571        & --    & 102m & 1494 \\
\hline
\end{tabular}

 \caption{Partitioning results for matrix factorization. The time reported by~\cite{valeriaMatrix} for this computation is 10440 seconds.}
 \label{tab:factor} 
\end{table}
Table~\ref{tab:cifar} shows the end-to-end numbers as
well as the numbers for the sixth stage, which is the heaviest. 
The number of gates are in millions, hence the suffix `m' in the last
three columns.
%For this DNN, the specialized \minion protocol takes 544 seconds and
%communicates 9272 Mb.
As with Table~\ref{tab:nn}, \tool generated generic 2PC protocol is
competitive with \minion here as well. Therefore,
we believe that with partitioning, \tool can scale to large
computations while maintaining performance
competitive with existing specialized protocols. In particular, for a
large enough DNN, \minion could run
out of memory but an appropriately partitioned \tool implementation would still
succeed.

@@

\subsection{Subsequent Work}
\TODO{....}

>>>>

\setlength\tabcolsep{2.8pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Dataset & $d$  & \thead{Prev \\ time\\ (s)} & \thead{Prev \\ comm\\ (KB)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm \\(KB)}  &  \thead{Num \\ gates} & LOC\\
\hline
Breast cancer & 30 & 0.3 & 36 & 0.1 & 0.3 & 25  & 727 & 20\\
\hline
Credit & 47 & 0.3 & 41 & 0.1 & 0.3 & 36  & 795 & 20\\
\hline
\end{tabular}
 \caption{Linear classification results. We compare \tool (LAN, WAN, Comm)
 with~\cite{shafindss} (Prev time, Prev comm).}
 \label{tab:lc} 
\end{table}

@@

\setlength\tabcolsep{2.5pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c|c|c |c|c|c|c|}
\hline
Dataset & $n$ & $F$ & \thead{Prev \\ time\\ (s)} & \thead{Prev \\ comm\\ (KB)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm \\(KB)} & \thead{Num \\ gates}  & LOC\\
\hline
Nursery & 5 & 9 & 1.5 & 0.2 & 0.1 & 0.4 & 0.6  & 73k & 50\\
\hline
Audiology & 24 & 70 & 3.9 & 2.0 & 1.5 & 2.9 & 37  & 4219k & 50\\
\hline
\end{tabular}
\caption{Na\"{i}ve Bayes results. We compare \tool (LAN, WAN, Comm)
 with~\cite{shafindss} (Prev time, Prev comm).}
 \label{tab:nb} 
\end{table}

@@

\begin{table}[t]
\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
Dataset  & $d$ & $N$ & \thead{Prev \\ time\\ (s)} & \thead{Prev \\ comm\\ (KB)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm \\(KB)}& \thead{Num \\ gates} & LOC\\
\hline
Nursery & 4 & 4 & 0.3 & 102 & 0.1 & 0.3 & 32 & 3324 & 20\\
\hline
ECG & 4 &  6 & 0.4 & 102 & 0.1 & 0.4 & 49  & 5002 & 20\\
\hline
\end{tabular}
\caption{Decision tree benchmarks.We compare \tool (LAN, WAN, Comm)
 with~\cite{wu} (Prev time, Prev comm).}
 \label{tab:dt} 
\end{table}

@@

\setlength\tabcolsep{2.5pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c |c|c|c|c|c|}
\hline
DNN  & \thead{Prev \\ time\\ (s)} & \thead{Prev \\ comm\\ (MB)} & \thead{LAN  \\ (s)} & \thead{WAN\\ (s)} & \thead{Comm \\(MB)} & \thead{Num \\ gates} & \thead{Model\\ size} & LOC\\
\hline
SecureML   &  1.1 & 15.8 & 0.7 & 1.7  & 76   &   366k   & 119k & 78\\
\hline
Cryptonets &  1.3 & 47.6 & 0.6 & 1.6  & 70    &  316k & 86k & 88\\
\hline
CNN        &  9.4 & 657.5& 5.1 & 11.6 & 501  & 9480k & 35k & 154\\
\hline
\end{tabular}

@@

% benchmark | size | gates | and | mul | depth  | length | comm | timeL | timeW
\setlength\tabcolsep{2.5pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c |c|c|c|c|c|c | c}
\hline
Classifier       & \thead{LAN  \\ (s)} & \thead{WAN \\(s)} & \thead{Comm \\(MB)}  & \thead{Num \\ And} & \thead{Num \\ Mul} & \thead{Num \\ gates} & \thead{Model \\size} & LOC\\
\hline
Regression &  0.1         & 0.7         & 5            & 2k    & 8k    &  35k    & 8k   & 38\\
\hline
CNN        &  30.5        & 60.3        & 2955         & 6082k & 4163k &  42104k & 3226k& 172\\
\hline
\end{tabular}

 \caption{Tensorflow tutorial benchmarks}
 \label{tab:tf} 
\end{table}
\setlength\tabcolsep{3.5pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c |c|c|c|c|c|c | c|}
\hline
Dataset       & \thead{LAN \\(s)} & \thead{WAN \\(s)} & \thead{Comm \\ (MB)}  & \thead{Num \\ And} & \thead{Num \\ Mul} & \thead{Num \\ gates} & depth & LOC\\
\hline
Chars4k    &  0.1         & 0.7         & 2            & 18k    & 3k    &  85k     & 1   & 89\\
\hline
USPS       &  0.2         & 0.9         & 4            & 62k    & 2k    &  285k    & 2   & 156\\
\hline
WARD       &  0.3         & 1.1         & 9            & 106k    & 8k    &  506k    & 3   & 283\\
\hline
\end{tabular}

@@

\setlength\tabcolsep{6pt}
\begin{table}
\footnotesize
\begin{tabular}{|c|c|c|c |c|c|c|}
\hline
           &  LAN (s) & WAN (s) & \thead{Comm \\ (MB)}  & \thead{Num \\ And} & \thead{Num \\ Mul} & \thead{Num \\ gates} \\
\hline
Total      &  265.6       & 647.5        & 40683       & 21m    & 61m    &  337m  \\
\hline
Stage 6    &  55.2        & 122.6        & 6744        & 12m    & 10m   &  98m  \\
\hline
\end{tabular}

@@

\begin{table}[t]
\footnotesize
\begin{tabular}{|c|c|c|c |c|c| c|}
\hline
  Stage         &  LAN (s) & WAN (s) & \thead{Comm \\ (MB)}  & depth & \thead{Num \\ gates} & LOC\\
\hline
1    &  175       & 662        & 29816       & 16370    & 33m    & 500  \\
\hline
2    &  193        & 1095        & 31945        & 30916    & 37m & 516 \\
\hline
3    &  178        & 627        & 29810        & 16369    & 32m  & 478  \\
\hline
Total    &  546      & 2384        & 91571        & --    & 102m & 1494 \\
\hline
\end{tabular}

 \caption{Partitioning results for matrix factorization. The time reported by~\cite{valeriaMatrix} for this computation is 10440 seconds.}
 \label{tab:factor} 
\end{table}
Table~\ref{tab:cifar} shows the end-to-end numbers as
well as the numbers for the sixth stage, which is the heaviest. 
The number of gates are in millions, hence the suffix `m' in the last
three columns.
%For this DNN, the specialized \minion protocol takes 544 seconds and
%communicates 9272 Mb.
As with Table~\ref{tab:nn}, \tool generated generic 2PC protocol is
competitive with \minion here as well. Therefore,
we believe that with partitioning, \tool can scale to large
computations while maintaining performance
competitive with existing specialized protocols. In particular, for a
large enough DNN, \minion could run
out of memory but an appropriately partitioned \tool implementation would still
succeed. For example, consider a large DNN with $n$ layers such that the circuit for only a single layer can  fit into memory. Then, \tool using partitioning can evaluate this large DNN in $n$ stages.

@@

\subsection{Subsequent Work}
Subsequent to our work, there have been improvements in the cryptographic backends.
For example, Gazelle describes specialized protocols for DNNs---which use a 
lattice-based packed additively homomorphic encryption scheme (PAHE) for arithmetic computations and garbled circuits for boolean computations---that can evaluate the CNN benchmark of Table~\ref{tab:nn} in 0.8 seconds (as opposed to
5.1 seconds taken by \tool when using ABY). Such advances in cryptography are
orthogonal to our contributions. In particular, we are interested in using Gazelle
as our backend when it becomes available. Furthermore, the authors of Gazelle remark:
``A final, very interesting and ambitious line
of work would be to build a compiler that allows us to easily
express arbitrary computations and automatically factor the
computation into PAHE and two-party primitives.''
\tool addresses this exact problem of factoring computations into
arithmetic and boolean parts.

### 2018-05-06 ccs/ex.tex
reviews incorporate

\tool source language is a simple, imperative language that enables
the programmers to express \mpc computations in terms of their
``ideal'' functionalities, without dealing with any cryptographic
details. The language provides multi-dimensional arrays \dg{with public indices}, conditional
expressions (the ternary $?\::$ operator), \ls{for}~loops,
\ls{if}~statements, and special syntax for input/output from each party.
\TODO{Add a justification for not having secret indices, public inputs etc. Unless there is a better place to have those.}

@@

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}) (in our usage
of ABY, boolean is synonymous with Yao, we elaborate in \sectionref{impl}).
\dg{We discuss the choices made by our compiler below in \sectionref{ccc}.}

@@

\subsection{Cryptographic cost-aware compiler}
\label{sec:ccc}
One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. Cryptographic cost of converting an arithmetic share to a boolean share requires computing a garbled circuit for addition that is linear in size. Similarly, the cost of converting from boolean to arithmetic is computing a subtraction circuit inside garbled circuit that is again linear in size. ABY analyses all of these costs by running microbenchmarks for basic operations and interconversions (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than  the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean \dg{($\sim9x$ time $\&$ $\sim20x$ comm. in LAN setting)}.
However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
Finally, all the boolean operations such as comparison, shifts, multiplexors, etc are done using Yao.
We note that doing an optimal split between arithmetic and boolean is an \dg{NP-hard} problem and in this work, we use some heuristics based on costs observed using microbenchmarking. Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.

>>>>

\tool source language is a simple, imperative language that enables
the programmers to express \mpc computations in terms of their
``ideal'' functionalities, without dealing with any cryptographic
details. The language provides multi-dimensional arrays with public indices, conditional
expressions (the ternary $?\::$ operator), \ls{for}~loops,
\ls{if}~statements, and special syntax for input/output from each party.

@@

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}) (in our usage
of ABY, boolean is synonymous with Yao, we elaborate in \sectionref{impl}).
We elaborate on cryptographic cost awareness in \sectionref{ccc}.

@@

\subsection{Cryptographic cost-aware compiler}
\label{sec:ccc}
One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. Cryptographic cost of converting an arithmetic share to a boolean share requires computing a garbled circuit for addition that is linear in size. Similarly, the cost of converting from boolean to arithmetic is computing a subtraction circuit inside garbled circuit that is again linear in size. ABY analyses all of these costs by running microbenchmarks for basic operations and interconversions (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than  the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean \dg{($\sim9x$ time $\&$ $\sim20x$ comm. in LAN setting)}. Since the performance gap between arithmetic and boolean is large, we believe that this choice is optimal for realistic network settings.
However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
Finally, all the boolean operations such as comparison, shifts, multiplexors, etc are done using Yao.
We note that doing an optimal split between arithmetic and boolean is an \dg{NP-hard} problem and in this work, we use some heuristics based on costs observed using microbenchmarking. 
For the smaller benchmarks of our evaluation, we wrote ABY code directly and the circuits
generated by our compiler had about the same size as the  hand written code. 
%Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.

### 2018-05-06 ccs/impl.tex
reviews incorporate

\vspace{-0.1in}
\section{Implementation}
\label{sec:impl}
We discuss some  implementation details of \tool.
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that
makes calls to the ABY
library~\cite{aby}. 
\TODO{Fix this!}
ABY provides a GMW-based~\cite{gmw} and a  Yao-based~\cite{yao} protocol for boolean computations.
Although \tool can generate code for both, we have observed better performance when using the latter
and use it in our evaluation.
We use $128$ bits of security and OT
extension-based arithmetic multiplication triplets generation. ABY
provides multi-threading support (for the offline phase of the \mpc
protocol); we leverage the support and use at most four threads in our
evaluation.

@@

We use an off-the-shelf solver
(SeaHorn~\cite{seahorn}) to bound check the array indices
($\models e < n$
in ({\sc {T-Read}}) and ({\sc{T-Write}}),
\figureref{compile}). We take the \tool source program and
translate it as an input to the solver. The solver takes less
than a minute on our largest benchmark to verify that all the array
accesses are in-bounds.

@@

\dg{remove addition?}
The compilation rules of \figureref{compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
Since \tool is aware of the cryptographic costs associated with these coercions,
it tries to minimize them using several optimizations.
For instance, if boolean shares of a variable are available in scope and the variable is involved in
an addition then \tool performs the addition in boolean rather than first coercing boolean to arithmetic
and then performing an arithmetic addition. 
%However, multiplication is always performed in arithmetic as the cost of a boolean multiplication is much higher than the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean~\cite{aby}.
Other optimizations include the standard ``common subexpression elimination"
optimization~\cite{dragonbook}.
On each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of inserting code to recompute them afresh.

>>>>

\vspace{-0.1in}
\section{Implementation}
\label{sec:impl}
We discuss some  implementation details of \tool.
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that
makes calls to the ABY
library~\cite{aby}. 
ABY provides support for Arithmetic computation based on \cite{autoS}, and boolean computations based on GMW~\cite{gmw} as well as Yao's garbled circuits~\cite{yao}. Although \tool can generate code for both kinds of boolean computations, we have observed better performance when using the garbled circuits
and use it in our evaluation. Hence, \tool generated code uses Arithmetic computation and garbled circuits based boolean computations.
We use $128$ bits of security and OT
extension-based arithmetic multiplication triplets generation. ABY
provides multi-threading support (for the offline phase of the \mpc
protocol); we leverage the support and use at most four threads in our
evaluation.

@@

We use an off-the-shelf solver
(SeaHorn~\cite{seahorn}) to bound check the array indices
($\models e < n$
in ({\sc {T-Read}}) and ({\sc{T-Write}}),
\figureref{compile}). We take the \tool source program and
translate it as an input C program to the solver. The solver takes less
than a minute on our largest benchmark to verify that all the array
accesses are in-bounds. This C program can also enable
validation of \tool generated protocols via differential testing~\cite{mckeeman,frigate}.

@@

The compilation rules of \figureref{compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
Since \tool is aware of the cryptographic costs associated with these coercions,
it tries to minimize them using several optimizations.
For instance, if boolean shares of a variable are available in scope and the variable is involved in
an addition then \tool performs the addition in boolean rather than first coercing boolean to arithmetic
and then performing an arithmetic addition. 
%However, multiplication is always performed in arithmetic as the cost of a boolean multiplication is much higher than the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean~\cite{aby}.
Other optimizations include the standard ``common subexpression elimination"
optimization~\cite{dragonbook}.
On each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of inserting code to recompute them afresh.

### 2018-05-06 ccs/intro.tex
reviews incorporate

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed either as a boolean
circuit~(\cite{yao,gmw}) or as an arithmetic circuit~(\cite{sss,viff,gentry}). 
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can either be expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
\dg{It is well-known that boolean circuits are not suitable for doing arithmetic operations such as integer multiplications but are unavoidable for boolean operations such as comparison \cite{aby,tasty,autoS,secureml,minionn,chameleon}.}
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%

@@

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. The generated protocols use combinations of
arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
that generic \mpc implementations are much more efficient than what they were believed to be. 
 %(up to a factor of 19x in our
%experiments, depending on the functionality) \nc{I added this but I
%  guess we are saying it many times, but might be nice to highlight
%  perf early no?} \aseem{My rationale was to save the numbers for
%  Evaluation summary and remain high-level here.} 
Below we describe
the salient features of \tool.

@@

\paragraph{Related Work.}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
and some have also developed tools that allow writing such
combinations (e.g. \cite{bogdanov,lone,tasty,autoS}). However, as Demmler et
al.~\cite{aby} observe, due
 to the high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. 
Additionally, these prior works provide informal languages
or libraries that lack formal semantics and static guarantees.
%Can be added to related work
% Kerschbaum et al.~\cite{autoS}
%provide a scheme to automatically assign homomorphic encryption or
%garbled circuits to each operators in a computation that has been expressed as a sequence of dyadic operations.
%They conjecture that the problem is NP hard and gave a linear programming based solution
%as well as a quadratic time greedy heuristic. \tool  uses a simpler constant time heuristic
%to assign arithmetic secret sharing or garbled circuits to sub-computations
%in a richer language with control flow statements such as loops and branches.
 We provide a detailed survey of related
work in \sectionref{related}.

>>>>

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed either as a boolean
circuit~(\cite{yao,gmw}) or as an arithmetic circuit~(\cite{sss,viff,gentry}). 
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can either be expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
It is well-known that boolean circuits are not suitable for doing arithmetic operations such as integer multiplications but are unavoidable for boolean operations such as comparison \cite{aby,tasty,autoS,secureml,minionn,chameleon}.
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%

@@

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. 
The generated protocols use combinations of
arithmetic and boolean circuits that introduce unique compilation challenges.
Standard compilers do not attempt to reason about or insert non-trivial type casts
and require the programmers to perform them explicitly. 
We back \tool with formal semantics that enable the compiler to
insert type conversions between boolean and arithmetic components
while maintaining provable correctness, security, and efficiency.
The automatically generated protocols have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
that generic \mpc implementations are much more efficient than what they were believed to be. 
 %(up to a factor of 19x in our
%experiments, depending on the functionality) \nc{I added this but I
%  guess we are saying it many times, but might be nice to highlight
%  perf early no?} \aseem{My rationale was to save the numbers for
%  Evaluation summary and remain high-level here.} 
Below we describe
the salient features of \tool.

@@

\paragraph{Related Work.}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
and some have also developed tools that allow writing such
combinations (e.g. \cite{bogdanov,lone,tasty,autoS}). However, as Demmler et
al.~\cite{aby} observe, due
 to the high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. 
Additionally, these prior works provide informal languages
or libraries that lack formal semantics and static guarantees.
Finally, we focus on the language
features necessary to implement machine learning applications.
In particular, we do not discuss declassification of
intermediate values or indexing into arrays at secret indices.
 Handling them requires additional complexity. For example,
Wysteria~\cite{wysteria} handles the former using dependent types
and ObliVM~\cite{oblivm} uses Oblivious RAM for the latter.
These situations arise seldomly in the machine learning applications that we consider:
intermediate values don't need to be declassified and arrays are traversed in an oblivious manner.

%\dg{Cite works like Wysteria~\cite{wysteria} for public inputs and declassification of intermediate values, ObliVM~\cite{oblivm} for hiding secret array indices using Oblivious RAM. But since the focus of this work is machine learning applications, we do not concern ourselves with these language complexities.}
%Can be added to related work
% Kerschbaum et al.~\cite{autoS}
%provide a scheme to automatically assign homomorphic encryption or
%garbled circuits to each operators in a computation that has been expressed as a sequence of dyadic operations.
%They conjecture that the problem is NP hard and gave a linear programming based solution
%as well as a quadratic time greedy heuristic. \tool  uses a simpler constant time heuristic
%to assign arithmetic secret sharing or garbled circuits to sub-computations
%in a richer language with control flow statements such as loops and branches.
 We provide a detailed survey of related
work in \sectionref{related}.
